Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-17 Grassmannian_cells.tex
Better remark?

\begin{remark}
  \label{rem:cell decompositions}
  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.

  By Theorem~\ref{vb}, to establish cell decompositions for the $\cG_{\tbff,\tbfg}$ it suffices to find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ for which $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells.
\end{remark}

>>>>

\begin{remark}
  \label{rem:cell decompositions}
  To apply Theorem~\ref{vb} and establish cell decompositions for the $\cG_{\tbff,\tbfg}$, we will find a cell decomposition of $\Gr_\tbff(M)\times\Gr_\tbfg(N)$ such that $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is a union of affine cells, giving an induced cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$.

  By Lemma~\ref{le:good partition}, the existence of cell decompositions for each $\cG_{\tbff,\tbfg}$ implies the existence of a cell decomposition for $\Gr_\tbfe(B)$.
  Indeed, we may take the affine cells of all the $\cG_{\tbff,\tbfg}$ as affine cells of $\Gr_\tbfe(B)$ with the natural lexicographic total order induced by taking cells from $\cG_{\tbff',\tbfg'}$ after those of $\cG_{\tbff,\tbfg}$ whenever $\tbff'\succ\tbff$.
\end{remark}
